### 2025-05-20 paper/main.tex
clean slate

\begin{abstract}
This paper introduces a novel quantum-classical hybrid system for medical image classification using neutral atom quantum processors. We present the Quantum Guided Autoencoder with Reservoir Surrogate (QGARS), which addresses the gradient barrier problem in quantum-classical hybrid learning by introducing a differentiable surrogate model that enables end-to-end training. Our approach leverages quantum reservoir computing principles with Rydberg atom arrays while optimizing feature encoding through a specialized autoencoder that jointly minimizes reconstruction error and maximizes quantum classification performance. We evaluate our approach on polyp detection and classification tasks, demonstrating superior performance compared to traditional dimensionality reduction techniques and standard quantum reservoir computing implementations. We further present detailed ablation studies analyzing the impact of various quantum parameters, guided learning coefficients, and surrogate model architectures. Our results suggest that quantum guidance can significantly enhance feature encoding for quantum processing, pointing toward a practical pathway for quantum advantage in medical image analysis.
\end{abstract}

@@

In this paper, we introduce the Quantum Guided Autoencoder with Reservoir Surrogate (QGARS) architecture, illustrated in Fig.~\ref{fig:system_architecture}. This approach combines classical deep learning with quantum reservoir computing to enable efficient medical image classification.

>>>>

\begin{abstract}
\end{abstract}

@@
